Eye Fitting Straight Lines in the Modern Era

### 2022-10-11 Eye-Fitting-Straight-Lines-in-the-Modern-Era.Rmd
made final revisions.

abstract: |
  How do statistical regression results compare to intuitive, visually fitted results? Fitting lines by eye through a set of points has been explored since the 20th century. Common methods of fitting trends by eye involve maneuvering a string, black thread, or ruler until the fit is suitable, then drawing the line through the set of points. In 2015, the New York Times introduced an interactive feature, called 'You Draw It', where readers were asked to input their own assumptions about various metrics and compare how these assumptions relate to reality. In this paper, we validate ‘You Draw It’ as a method for graphical testing, comparing results to the less technological method utilized in \citet{mosteller1981eye} and extending that study with formal statistical analysis methods. Results were consistent with those found in the previous study; when shown points following a linear trend, participants tended to fit the slope of the first principal component over the slope of the least-squares regression line. This trend was most prominent when shown data simulated with larger variances. This study reinforces the differences between intuitive visual model fitting and statistical model fitting, providing information about human perception as it relates to the use of statistical graphics.

@@

We need human testing of graphics in order to draw broad conclusions, develop guidelines for graphical design, and improve graphical communication.
Studies might ask participants to identify differences in graphs, read information off of a chart accurately, use data to make correct real-world decisions, or predict the next few observations.
All of these types of tests require different levels of use and manipulation of the information being presented in the chart. 
Early research studies considered graphs from a psychological perspective [@spence1990visual; @lewandowsky1989perception], testing participants' abilities to detect a stimulus or a difference between two stimuli. Psychophysical methods have been used to test graphical perception, as in @vanderplas2015signs, which used the method of adjustment - a technique which requires participants to alter a changing stimulus to match a given constant stimuli [@gescheider_1997]- to estimate the magnitude of the impact of the sine illusion.
However, there are more modern testing methods that have been developed since the heyday of psychophysics.

One major development in statistical graphics which led to more advanced testing methods is Wilkinson’s Grammar of Graphics [@wilkinson2013grammar].
The Grammar of Graphics serves as the fundamental framework for data visualization with the notion that graphics are built from the ground up by specifying exactly how to create a particular graph from a given data set.
Visual representations are constructed through the use of “tidy data” which is characterized as a data set in which each variable is in its own column, each observation is in its own row, and each value is in its own cell [@wickham2016r].
Graphics are viewed as a mapping from variables in a data set (or statistics computed from the data) to visual attributes such as the axes, colors, shapes, or facets on the canvas in which the chart is displayed.
Software, such as Hadley Wickham’s ggplot2 [@wickham2011ggplot2], aims to implement the framework of creating charts and graphics as the Grammar of Graphics recommends.

@@

In @ciccione2021can, participants were asked to judge trends, estimate slopes, and conduct extrapolation.
To estimate slopes, participants were asked to report the slope of the best-fitting regression line using a track-pad to adjust the tilt of a line on the screen.
Results indicated the slopes participants reported were always in excess of the ideal slopes, both in the positive and in the negative direction, and those biases increase with noise and with number of points. 
This supports the results found in @mosteller1981eye and suggest that participants might use Deming regression [@deming1943statistical; @linnet1998performance; @martin2000general], which minimizes the Euclidean distance of points from the line, when fitting a line to a noisy scatterplot.

@@

Participants were recruited through through Twitter, Reddit, and direct email in May 2021.
A total of 35 individuals completed `r length(unique(eyefitting_model_data$plot_id))` unique 'You Draw It' task plots.
Data were collected as a part of a pilot study meant to test the applet; therefore, either voluntary participant dropout or disconnection from a server not designed to accommodate large magnitudes of participants resulted in missing plots in our data set for analysis.
All participants had normal or corrected to normal vision and signed an informed consent form.
The experimental tasks took approximately 15 minutes to complete.
As this is a pilot study, participants from Twitter and Reddit pages related to data visualization voluntarily completed the study and likely had an interest in fields related to statistics and wanted to help advance research in graphics.
While this study does utilize a convenience sample, as this is primarily a perceptual task, previous results have found few differences between expert and non-expert participants in this context [@vanderplas2015spatial].
These data were collected to validate this method of graphical testing, with the hopes of providing a new tool to assess graphical perception interactively.
Participants completed the experiment on their own computers in an environment of their choosing. The experiment was conducted and distributed through a Shiny application [@shinyPkg] found at [https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/](https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/).

@@

In the study, participants were shown an interactive scatterplot \pcref{fig:ydi-stimuli} along with the prompt, “Use your mouse to fill in the trend in the yellow box region.”
The yellow box region moved along as the user drew their trend-line, providing a visual cue which indicates where the user still needed to complete a trend line. After the entire domain had been visually estimated or predicted, the yellow shaded region disappeared, indicating the participant had completed the task.
Data Driven Documents (D3), a JavaScript-based graphing framework that facilitates user interaction, was used to create the 'You Draw It' visual. 
In order to allow for user interaction and data collection, we integrated the D3 visual into Shiny using the `r2d3` R package [@r2d3].
While the interface is highly customized to this particular task, we hope to generalize the code and provide a Shiny widget in an R package soon.

@@

All data processing was conducted in R software environment for statistical computing and graphics [@Rsoftware]. 
A total of $N = 30$ points $(x_i, y_i), i = 1,...,N$ were generated for $x_i \in [x_{min}, x_{max}]$ where $x$ and $y$ have a linear relationship.
Data were simulated based on the point-slope form of a linear model with additive errors: 
\begin{align}
y_i = \beta_1(x_i-\bar{x}) + y_{\bar{x}} + e_i \\
\text{with } e_i & \sim N(0, \sigma^2). \nonumber
\end{align}

where $\beta_1$ represents the slope of the trend and $y_{\bar{x}}$ represents the $y$ value at the mean of the generated $x$ values. Model equation parameters, $\beta_1$, $y_{\bar{x}}$, and parameter choice letter names (S, F, V, N), were selected to reflect the four data sets used and labeled in @mosteller1981eye \pcref{tab:eyefitting-parameters}. The point $(x, y_{\bar{x})}$ was used in the point-slope equation of a line.
Parameter choices S, F, and N simulated data across a domain of 0 to 20. 
Parameter choice F produced a trend with a positive slope and a large variance while N had a negative slope and a large variance. 
In comparison, S showed a trend with a positive slope and a small variance while V yielded a steep positive slope with a small variance over the domain of 4 to 16. 
\cref{fig:eyefitting-simplot} illustrates an example of simulated data for all four parameter choices intended to reflect the trends in @mosteller1981eye.
Aesthetic design choices were made consistent across each of the interactive 'You Draw It' task plots. 
The y-axis range extended 10\% beyond (above and below) the range of the simulated data points to allow for users to draw outside the simulated data set range and avoid anchoring their lines to the corners of the plot.

@@

Due to the randomness in the data generation process, the actual slope of the linear regression line fit through the simulated points could differ from the predetermined slope.
Therefore, we fit an OLS regression to each scatterplot to obtain estimated parameters $\hat\beta_{0,OLS}$ and $\hat\beta_{1,OLS}$.
Fitted values, $\hat y_{k,OLS}$, were then obtained every 0.25 increment across the domain from the OLS regression equation, $\hat y_{k,OLS} = \hat\beta_{0,OLS} + \hat\beta_{1,OLS} x_k$, for $k = 1, ..., 4 x_{max} +1$. 
The PA regression slope, $\hat\beta_{1,PA}$, and y-intercept, $\hat\beta_{0,PA}$, were determined using the `mcreg` function in the mcr package in R [@mcr_pkg] which implements Deming regression (equivalent to a regression based on the slope of the first principal axis).
Fitted values, $\hat y_{k,PA}$ were then obtained every 0.25 increment across the domain from the PA regression equation, $\hat y_{k,PA} = \hat\beta_{0,PA} + \hat\beta_{1,PA} x_k$, for $k = 1, ..., 4 x_{max} +1$.

@@

The intent of this research was to adapt 'You Draw It' from the New York Times feature as a tool and method for testing graphics and introduce a method for statistically modeling the participant drawn lines.
We provided support for the validity of the 'You Draw It' method by replicating the study found in @mosteller1981eye.
Using generalized additive mixed models, we assessed the deviation of the participant drawn lines from the statistically fitted regression lines.
Our results found that when shown points following a linear trend, participants visually fit a regression line that mimics the first principal axis regression as opposed to ordinary least squares regression. 
Data simulated with a larger variance provided strong support for a participants tendency to visually fit the first principal axis regression.
We utilized modern technology to replicate a study conducted 40 years ago, and strengthened the original results with current analysis methods which allow for more flexibility and sophistication.
Our results indicate that participants minimized the distance from their drawn regression line over both the $x$ and $y$ axis simultaneously. 
<!-- These results provide support that humans perform "ensemble perception" in a statistical graphic setting. -->
We allowed participants to draw trend lines that deviated from a straight line and gained an insight into the curvature the human eye perceives in a set of points.
Researchers in cognitive and human movement sciences have found that human arm movement is a complex task [@miall1995curvature; @rousset2015study].
The 'You Draw It' method described in this paper uses *indirect interaction* in which the mouse position and resulting visual line on the screen are dissociated.
Therefore, curvature found in participant drawn lines from a straight lines could potentially be explained by the lack of coordination which results from the eye-hand dissociation from indirect drawing and the distortion of visual perception affecting the curvature of movements.
Additionally, there is a training effect related to the completion of the 'You Draw It' task - the movement of the line must be slow so that the visual representation on the screen can accurately capture each movement. 
@de1991misdirections conducted a study in which participants moved their hand slowly from an initial position in front of them to a visual target (movement task); they were then asked to repeat the task using different sizes of pointers (perceptual task).
Their results indicated that deviations from the shortest pointers were comparable to those of the movement task, but that bias increased as the length of the pointer increased.
While we suggested participants use a mouse to complete the study, we could not require the use; therefore, some participants may have used a track-pad and results may have been influenced by the pressure placed on their track-pad [@easton1978finger].
In cognitive psychology, @cui_2018 studied the improvement in estimating correlations in scatter plots through perceptual learning interventions.  
Their study provided support for an improved proficiency in correlation estimation after training.
We used a randomized complete design experimental structure, while @mosteller1981eye implemented a latin square design to test for an order effect due to practice.

@@

This study provided a basis for the use of 'You Draw It' as a tool for testing statistical graphics and introduced a method for statistically modeling participant drawn lines using generalized additive mixed models.
Additional studies related to the validation and use of the tool would be useful for providing insight into explanations of biases introduced by the task such as the deviation from a straight line.
For instance, a variation on the current study could compare manual adjustment methods such as shifting and rotating a horizontal line segment until the fit is suitable to the 'You Draw It' method on the same set of data. This might explain the large deviation from the participant drawn line as $x$ approaches 20.
Another useful extension study would be to compare the 'You Draw It' method as conducted by direct interaction - using a digital pen on a tablet - to indirect interaction - using a computer mouse to relate to a pointer on the screen. 
Previous studies investigated human ability to perform regressions over scatterplots with outliers and found participant estimated trend lines to be closer to a robust trend line than the statistically fitted trend line where outliers were included [@bobko_1979; @correll_2017].
This work could provide an extension and further evaluate the perceptual system's resistance to outliers by allowing participants to deviate from a straight line, potentially capturing the outlier(s).
<!-- Further extensions to this work might ask participants to draw a trend-line through scatterplots with one (or multiple) extreme outliers in order to further evaluate the perceptual system's resistance to outliers [@bobko_1979; @correll_2017]. -->
While the focus of this study was on drawing linear trend-lines, further investigation is necessary to implement this method in non-linear settings and with real data in order to facilitate scientific communication - a strength of the combination of the flexible 'You Draw It' method and GAMM analysis method.
@ciccione2021can evaluated human ability to extrapolate data from trends by asking participants to provide a single point estimate; this tool could be used to evaluate a continuous extrapolation of points from a trend line for various linear and non-linear data structures.
In the future, we intend to create an R package designed for easy implementation of 'You Draw It' task plots in order to make this tool accessible to other researchers.

@@

<!-- + **Study Applet:** The shiny app used to conduct the study can be accessed at  [https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/](https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/). -->
<!-- + **RShiny Applet Code:** The code used to create the RShiny Applet for data collection can be found at [https://github.com/earobinson95/you-draw-it-validation-applet(https://github.com/earobinson95/you-draw-it-validation-applet). -->
+ **Participant Data:** De-identified participant data collected in the study and used for analyses (eyefitting-model-data.csv).
<!-- `eyefitting-model-data.csv` or may be downloaded from GitHub at  [https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/data](https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/data).  -->
+ **Data Analysis Code:** The code used to replicate the analysis in this paper (you-draw-it-eyefitting-analysis.Rmd).
<!-- or found at [https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/analysis/you-draw-it-eyefitting-analysis.Rmd](https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/supplementary-materials/you-draw-it-eyefitting-analysis.Rmd). -->
+ **README:** File containing detailed descriptions of the supplementary material (README.html).

>>>>

abstract: |
  How do statistical regression results compare to intuitive, visually fitted results? Fitting lines by eye through a set of points has been explored since the 20th century. Common methods of fitting trends by eye involve maneuvering a string, black thread, or ruler until the fit is suitable, then drawing the line through the set of points. In 2015, the New York Times introduced an interactive feature, called 'You Draw It', where readers were asked to input their own assumptions about various metrics and compare how these assumptions relate to reality. In this paper, we validate ‘You Draw It’ as a method for graphical testing, comparing results to the less technological method utilized in \citet{mosteller1981eye} and extending that study with formal statistical analysis methods. Results were consistent with those found in the previous study; when shown points following a linear trend, participants tended to fit the slope of the principal axis over the slope of the least-squares regression line. This trend was most prominent when shown data simulated with larger variances. This study reinforces the differences between intuitive visual model fitting and statistical model fitting, providing information about human perception as it relates to the use of statistical graphics.

@@

We need human testing of graphics in order to draw broad conclusions, develop guidelines for graphical design, and improve graphical communication.
Studies might ask participants to identify differences in graphs, read information off of a chart accurately, use data to make correct real-world decisions, or predict the next few observations.
All of these types of tests require different levels of use and manipulation of the information being presented in the chart. 
Early research studies considered graphs from a psychological perspective [@spence1990visual; @lewandowsky1989perception], testing participants' abilities to detect a stimulus or a difference between two stimuli. Psychophysical methods have been used to test graphical perception, as in @vanderplas2015signs, which used the method of adjustment - a technique which requires participants to alter a changing stimulus to match a given constant stimuli [@gescheider_1997] - to estimate the magnitude of the impact of the sine illusion.
However, there are more modern testing methods that have been developed since the heyday of psychophysics.

One major development in statistical graphics which led to more advanced testing methods is Wilkinson’s Grammar of Graphics [@wilkinson2013grammar].
The Grammar of Graphics serves as the fundamental framework for data visualization with the notion that graphics are built from the ground up by specifying exactly how to create a particular graph from a given data set.
Visual representations are constructed through the use of “tidy data” which is characterized as a data set in which each variable is in its own column, each observation is in its own row, and each value is in its own cell [@wickham2016r].
Graphics are viewed as a mapping from variables in a data set (or statistics computed from the data) to visual attributes such as the axes, colors, shapes, or facets on the canvas in which the chart is displayed.
Software, such as Hadley Wickham’s `ggplot2` package in R [@wickham2011ggplot2], aims to implement the framework of creating charts and graphics as the Grammar of Graphics recommends.

@@

In @ciccione2021can, participants were asked to judge trends, estimate slopes, and conduct extrapolation.
To estimate slopes, participants were asked to report the slope of the best-fitting regression line using a track-pad to adjust the tilt of a line on the screen.
Results indicated the slopes participants reported were always in excess of the ideal slopes, both in the positive and in the negative direction, and those biases increase with noise and with number of points. 
This supports the results found in @mosteller1981eye and suggest that participants might use Deming regression [@deming1943statistical; @linnet1998performance; @martin2000general], which is equivalent to the principal axis and minimizes the Euclidean distance of points from the line, when fitting a line to a noisy scatterplot.

@@

Participants were recruited through Twitter, Reddit, and direct email in May 2021.
A total of 35 individuals completed `r length(unique(eyefitting_model_data$plot_id))` unique 'You Draw It' task plots.
Data were collected as a part of a pilot study meant to test the applet; therefore, either voluntary participant dropout or disconnection from a server not designed to accommodate large magnitudes of participants resulted in missing plots in our data set for analysis.
All participants had normal or corrected to normal vision and signed an informed consent form.
The experimental tasks took approximately 15 minutes to complete.
As this is a pilot study, participants from Twitter and Reddit pages related to data visualization voluntarily completed the study and likely had an interest in fields related to statistics and wanted to help advance research in graphics.
While this study does utilize a convenience sample, as this is primarily a perceptual task, previous results have found few differences between expert and non-expert participants in this context [@vanderplas2015spatial].
These data were collected to validate this method of graphical testing, with the hopes of providing a new tool to assess graphical perception interactively.
Participants completed the experiment on their own computers in an environment of their choosing. The experiment was conducted and distributed through a R Shiny application [@shinyPkg] found at [https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/](https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/).

@@

In the study, participants were shown an interactive scatterplot \pcref{fig:ydi-stimuli} along with the prompt, “Use your mouse to fill in the trend in the yellow box region.”
The yellow box region moved along as the user drew their trend-line, providing a visual cue which indicates where the user still needed to complete a trend line. After the entire domain had been visually estimated or predicted, the yellow shaded region disappeared, indicating the participant had completed the task.
Data Driven Documents (D3), a JavaScript-based graphing framework that facilitates user interaction, was used to create the 'You Draw It' visual. 
In order to allow for user interaction and data collection, we integrated the D3 visual into R Shiny using the `r2d3` R package [@r2d3].
While the interface is highly customized to this particular task, we hope to generalize the code and provide a Shiny widget in an R package soon.

@@

All data processing was conducted in R software environment for statistical computing and graphics [@Rsoftware]. 
A total of $N = 30$ points $(x_i, y_i), i = 1,...,N$ were generated for $x_i \in [x_{min}, x_{max}]$ where $x$ and $y$ have a linear relationship.
Data were simulated based on the point-slope form of a linear model with additive errors: 
\begin{align}
y_i = \beta_1(x_i-\bar{x}) + y_{\bar{x}} + e_i \\
\text{with } e_i & \sim N(0, \sigma^2). \nonumber
\end{align} 
where $\beta_1$ represents the slope of the trend and $y_{\bar{x}}$ represents the $y$ value at the mean of the generated $x$ values. Model equation parameters, $\beta_1$, $y_{\bar{x}}$, and parameter choice letter names (S, F, V, N), were selected to reflect the four data sets used and labeled in @mosteller1981eye \pcref{tab:eyefitting-parameters}. The point $(x, y_{\bar{x})}$ was used in the point-slope equation of a line.
Parameter choices S, F, and N simulated data across a domain of 0 to 20. 
Parameter choice F produced a trend with a positive slope and a large variance while N had a negative slope and a large variance. 
In comparison, S showed a trend with a positive slope and a small variance while V yielded a steep positive slope with a small variance over the domain of 4 to 16. 
\cref{fig:eyefitting-simplot} illustrates an example of simulated data for all four parameter choices intended to reflect the trends in @mosteller1981eye.
Aesthetic design choices were made consistent across each of the interactive 'You Draw It' task plots. 
The $y$-axis range extended 10\% beyond (above and below) the range of the simulated data points to allow for users to draw outside the simulated data set range and avoid anchoring their lines to the corners of the plot.

@@

Due to the randomness in the data generation process, the actual slope of the linear regression line fit through the simulated points could differ from the predetermined slope.
Therefore, we fit an OLS regression to each scatterplot to obtain estimated parameters $\hat\beta_{0,OLS}$ and $\hat\beta_{1,OLS}$.
Fitted values, $\hat y_{k,OLS}$, were then obtained every 0.25 increment across the domain from the OLS regression equation, $\hat y_{k,OLS} = \hat\beta_{0,OLS} + \hat\beta_{1,OLS} x_k$, for $k = 1, ..., 4 x_{max} +1$. 
The PA regression slope, $\hat\beta_{1,PA}$, and $y$-intercept, $\hat\beta_{0,PA}$, were determined using the `mcreg` function in the mcr package in R [@mcr_pkg] which implements Deming regression (equivalent to a regression based on the slope of the principal axis).
Fitted values, $\hat y_{k,PA}$ were then obtained every 0.25 increment across the domain from the PA regression equation, $\hat y_{k,PA} = \hat\beta_{0,PA} + \hat\beta_{1,PA} x_k$, for $k = 1, ..., 4 x_{max} +1$.

@@

The intent of this research was to adapt 'You Draw It' from the New York Times feature as a tool and method for testing graphics and introduce a method for statistically modeling the participant drawn lines.
We provided support for the validity of the 'You Draw It' method by replicating the study found in @mosteller1981eye.
Using generalized additive mixed models, we assessed the deviation of the participant drawn lines from the statistically fitted regression lines.
Our results found that when shown points following a linear trend, participants visually fit a regression line that mimics the principal axis regression line as opposed to ordinary least squares regression line. 
Data simulated with a larger variance provided strong support for a participants tendency to visually fit the first principal axis regression.
We utilized modern technology to replicate a study conducted 40 years ago, and strengthened the original results with current analysis methods which allow for more flexibility and sophistication.
Our results indicate that participants minimized the distance from their drawn regression line over both the $x$ and $y$ axis simultaneously. 
<!-- These results provide support that humans perform "ensemble perception" in a statistical graphic setting. -->
We allowed participants to draw trend lines that deviated from a straight line and gained an insight into the curvature the human eye perceives in a set of points.

Researchers in cognitive and human movement sciences have found that human arm movement is a complex task [@miall1995curvature; @rousset2015study].
The 'You Draw It' method described in this paper uses *indirect interaction* in which the mouse position and resulting visual line on the screen are dissociated.
Therefore, curvature found in participant drawn lines from a straight lines could potentially be explained by the lack of coordination which results from the eye-hand dissociation from indirect drawing and the distortion of visual perception affecting the curvature of movements.
Additionally, there is a training effect related to the completion of the 'You Draw It' task - the movement of the line must be slow so that the visual representation on the screen can accurately capture each movement. 
@de1991misdirections conducted a study in which participants moved their hand slowly from an initial position in front of them to a visual target (movement task); they were then asked to repeat the task using different sizes of pointers (perceptual task).
Their results indicated that deviations from the shortest pointers were comparable to those of the movement task, but that bias increased as the length of the pointer increased.
While we suggested participants use a mouse to complete the study, we could not require the use; therefore, some participants may have used a track-pad and results may have been influenced by the pressure placed on their track-pad [@easton1978finger].
In cognitive psychology, @cui_2018 studied the improvement in estimating correlations in scatter plots through perceptual learning interventions.
Results form their study provided support for an improved proficiency in correlation estimation after training.
We used a randomized complete design experimental structure, while @mosteller1981eye implemented a latin square design to test for an order effect due to practice.

@@

This study provided a basis for the use of 'You Draw It' as a tool for testing statistical graphics and introduced a method for statistically modeling participant drawn lines using generalized additive mixed models.
Additional studies related to the validation and use of the tool would be useful for providing insight into explanations of biases introduced by the task such as the deviation from a straight line.
For instance, a variation on the current study could compare manual adjustment methods such as shifting and rotating a horizontal line segment until the fit is suitable to the 'You Draw It' method on the same set of data. This might explain the large deviation from the participant drawn line as $x$ approaches 20.
Another useful extension study would be to compare the 'You Draw It' method as conducted by direct interaction - using a digital pen on a tablet - to indirect interaction - using a computer mouse to relate to a pointer on the screen. 
Previous studies investigated human ability to perform regressions over scatterplots with outliers and found participant estimated trend lines to be closer to a robust trend line than the statistically fitted trend line where outliers were included [@bobko_1979; @correll_2017].
The work in this paper could provide an extension and further evaluate the perceptual system's resistance to outliers by allowing participants to deviate from a straight line, potentially capturing the outlier(s).
<!-- Further extensions to this work might ask participants to draw a trend-line through scatterplots with one (or multiple) extreme outliers in order to further evaluate the perceptual system's resistance to outliers [@bobko_1979; @correll_2017]. -->
While the focus of this study was on drawing linear trend lines, further investigation is necessary to implement this method in nonlinear settings and with real data in order to facilitate scientific communication - a strength of the combination of the flexible 'You Draw It' method and GAMM analysis method.
@ciccione2021can evaluated human ability to extrapolate data from trends by asking participants to provide a single point estimate; this tool could be used to evaluate a continuous extrapolation of points from a trend line for various linear and nonlinear data structures.
In the future, we intend to create an R package designed for easy implementation of 'You Draw It' task plots in order to make this tool accessible to other researchers.

@@

<!-- + **Study Applet:** The shiny app used to conduct the study can be accessed at  [https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/](https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/). -->
<!-- + **RShiny Applet Code:** The code used to create the RShiny Applet for data collection can be found at [https://github.com/earobinson95/you-draw-it-validation-applet(https://github.com/earobinson95/you-draw-it-validation-applet). -->
+ **Participant Data:** De-identified participant data collected in the study and used for analyses (eyefitting-model-data.csv).
<!-- `eyefitting-model-data.csv` or may be downloaded from GitHub at  [https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/data](https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/data).  -->
+ **Data Analysis Code:** The code used to replicate the analysis in this paper (you-draw-it-eyefitting-analysis.Rmd).
<!-- or found at [https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/analysis/you-draw-it-eyefitting-analysis.Rmd](https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/supplementary-materials/you-draw-it-eyefitting-analysis.Rmd). -->
+ **readme:** File containing detailed descriptions of the supplementary material (README.html).
